Efficient Handling of String-Number Conversion

### 2019-11-23 draft.tex
sec 6

The theorem can be proved by a structural induction over $\insc$.
However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ than just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.  
Particularly, we will need to
 ensure that $\underf \dr \phi$ captures exactly all $\dr$-encodings of $\semof \phi^\dr$
(indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf \dr {\phi} \land \underf \dr {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^\dr$).
%To formalize this correctness argument, we need the notion of 
%%
%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
%%
%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.  
%\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
%
%Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
%%
%then an $R$-encoding of $I \cup I'$ is any interpretation $e \cup I$ with  $e:V_R \cup \#V_R \cup \Simga_\epsilon$ 
%such that $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$. That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
%
%
%and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
%
The inductive argument needed in the correctness proof of the under-approximation then reads as
$$\semof{\underf \dr \phi}_{V_\dr\cup V_{\#\dr}}  = \encode \dr{\semof{\phi}}$$ 
%
In the next sections, 
we will formulate the corresponding correctness lemma for flattening constructed from each type of atomic string constraints.
%
We note that the restriction of the semantics of $\underf \dr \phi$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.

>>>>

The theorem can be proved by a structural induction over $\insc$.
However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ than just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.  
Particularly, we will need to
 ensure that $\underf \dr \phi$ captures exactly all $\dr$-encodings of $\semof \phi^\dr$
(indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf \dr {\phi} \land \underf \dr {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^\dr$).
%To formalize this correctness argument, we need the notion of 
%%
%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
%%
%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.  
%\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
%
%Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
%%
%then an $R$-encoding of $I \cup I'$ is any interpretation $e \cup I$ with  $e:V_R \cup \#V_R \cup \Simga_\epsilon$ 
%such that $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$. That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
%
%
%and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
%
The inductive argument needed in the correctness proof of the under-approximation then reads as
$$\semof{\underf \dr \phi}_{V_\dr\cup V_{\#\dr}}  = \encode \dr{\semof{\phi}}$$ 
%
In the next sections, 
we will formulate the corresponding correctness lemma for flattening constructed from each type of atomic string constraints.
%
We note that the restriction of $\semof{\underf \dr \phi}$ to $V_\dr\cup V_{\#\dr}$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.
